---
title       : Predict Your Vehicle's 1/4 Mile Time
subtitle    : a simple app using R and shiny
author      : Michael Green
job         : 
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Predict Your Vehicle's 1/4 Mile Time

* Don't have access to a test track?
* Dealer won't let you 'see what this car can really do' on your test drive?
* Predict your vehicle's 1/4 mile time with this new app!

--- .class #id 

## The Data

* This app uses the [mtcars](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) data set in R to fit a linear model to predict 1/4 mile time given vehicle horsepower and weight.

* The relationship between hp and weight and 1/4 mile speed can be seen here:


```{r, echo=FALSE, fig.width=10, fig.height=5}
library(ggplot2)
library(gridExtra)

plot1 <- ggplot(mtcars, aes(x=hp, y=qsec)) + geom_point(shape=1) +
        scale_colour_hue(l=50) + # Use a slightly darker palette than normal
        geom_smooth(method=lm, fullrange=TRUE) + # Add linear regression lines
        theme(legend.title=element_blank()) +
        ylab("1/4 mile time (sec)")
        
plot2 <- ggplot(mtcars, aes(x=wt, y=qsec)) + geom_point(shape=1) +
        scale_colour_hue(l=50) + # Use a slightly darker palette than normal
        geom_smooth(method=lm, fullrange=TRUE)  + # Add linear regression lines
        theme(legend.title=element_blank()) +
        xlab("wt/1000lbs") +
        ylab("1/4 mile time (sec)")
                    

grid.arrange(plot1, plot2, ncol=2)
```

---

## The Predictor Algorithm

* First we fit a linear model:
```{r}
fit1 <- lm(qsec~hp + wt, data = mtcars)
```

* We can predict the 1/4 mile time for a vehicle of 2000lbs and 200hp:
```{r}
predict(fit1, data.frame(hp = 200, wt = 2),
        interval = "prediction")
```

* Notice the prediction interval is several seconds. But if you want more precision, you will have to pay for the upgraded app!

---

## The App

* The app is built using the shiny library in R, with two files:
* ui.R 
    + Creates a sidebar that allows user input, via a slider, for hp and wt. 
    + Creates a main panel that has 2 tabs: Results and About. 
    + The About tab describes the function the app performs. 
* server.R
    + Does the math.
* These files can be found at my github repo here:
    + https://github.com/mykelagrene/Rdataproducts
* Use the app:
    + https://mykelagrene.shinyapps.io/project
* Enjoy!




